# Clustering

## K-Means Clustering

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Importing the dataset

**Python**

```{python}
dataset = pd.read_csv('Mall_Customers.csv')
X = dataset.iloc[:, [3, 4]].values
```

**R**

```{r}
dataset = read.csv('Mall_Customers.csv')
dataset = dataset[4:5]
```

### Using the elbow method to find the optimal number of clusters

**Python**

```{python}
from sklearn.cluster import KMeans
wcss = []
for i in range(1, 11):
    kmeans = KMeans(n_clusters = i, init = 'k-means++', random_state = 42)
    kmeans.fit(X)
    wcss.append(kmeans.inertia_)
plt.plot(range(1, 11), wcss)
plt.title('The Elbow Method')
plt.xlabel('Number of clusters')
plt.ylabel('WCSS')
plt.show()
```

**R**

```{r}
set.seed(6)
wcss = vector()
for (i in 1:10) wcss[i] = sum(kmeans(dataset, i)$withinss)
plot(1:10,
     wcss,
     type = 'b',
     main = paste('The Elbow Method'),
     xlab = 'Number of clusters',
     ylab = 'WCSS')
```

### Training the K-Means model on the dataset/Fitting K-Means to the dataset

**Python**

```{python}
kmeans = KMeans(n_clusters = 5, init = 'k-means++', random_state = 42)
y_kmeans = kmeans.fit_predict(X)
```

**R**

```{r}
set.seed(29)
kmeans = kmeans(x = dataset, centers = 5)
y_kmeans = kmeans$cluster
```

### Visualising the clusters

**Python**

```{python}
plt.scatter(X[y_kmeans == 0, 0], X[y_kmeans == 0, 1], s = 100, c = 'red', label = 'Cluster 1')
plt.scatter(X[y_kmeans == 1, 0], X[y_kmeans == 1, 1], s = 100, c = 'blue', label = 'Cluster 2')
plt.scatter(X[y_kmeans == 2, 0], X[y_kmeans == 2, 1], s = 100, c = 'green', label = 'Cluster 3')
plt.scatter(X[y_kmeans == 3, 0], X[y_kmeans == 3, 1], s = 100, c = 'cyan', label = 'Cluster 4')
plt.scatter(X[y_kmeans == 4, 0], X[y_kmeans == 4, 1], s = 100, c = 'magenta', label = 'Cluster 5')
plt.scatter(kmeans.cluster_centers_[:, 0], kmeans.cluster_centers_[:, 1], s = 300, c = 'yellow', label = 'Centroids')
plt.title('Clusters of customers')
plt.xlabel('Annual Income (k$)')
plt.ylabel('Spending Score (1-100)')
plt.legend()
plt.show()
```

**R**

```{r}
library(cluster)
clusplot(dataset,
         y_kmeans,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')
```

## Hierarchical Clustering

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Importing the dataset

**Python**

```{python}
dataset = pd.read_csv('Mall_Customers.csv')
X = dataset.iloc[:, [3, 4]].values
```

**R**

```{r}
dataset = read.csv('Mall_Customers.csv')
dataset = dataset[4:5]
```

### Using the dendrogram to find the optimal number of clusters

**Python**

```{python}
import scipy.cluster.hierarchy as sch
dendrogram = sch.dendrogram(sch.linkage(X, method = 'ward'))
plt.title('Dendrogram')
plt.xlabel('Customers')
plt.ylabel('Euclidean distances')
plt.show()
```

**R**

```{r}
dendrogram = hclust(d = dist(dataset, method = 'euclidean'), method = 'ward.D')
plot(dendrogram,
     main = paste('Dendrogram'),
     xlab = 'Customers',
     ylab = 'Euclidean distances')
```

### Training the Hierarchical Clustering model on the dataset/Fitting Hierarchical Clustering to the dataset

**Python**

```{python}
from sklearn.cluster import AgglomerativeClustering
hc = AgglomerativeClustering(n_clusters = 5, affinity = 'euclidean', linkage = 'ward')
y_hc = hc.fit_predict(X)
```

**R**

```{r}
hc = hclust(d = dist(dataset, method = 'euclidean'), method = 'ward.D')
y_hc = cutree(hc, 5)
```

### Visualising the clusters

**Python**

```{python}
plt.scatter(X[y_hc == 0, 0], X[y_hc == 0, 1], s = 100, c = 'red', label = 'Cluster 1')
plt.scatter(X[y_hc == 1, 0], X[y_hc == 1, 1], s = 100, c = 'blue', label = 'Cluster 2')
plt.scatter(X[y_hc == 2, 0], X[y_hc == 2, 1], s = 100, c = 'green', label = 'Cluster 3')
plt.scatter(X[y_hc == 3, 0], X[y_hc == 3, 1], s = 100, c = 'cyan', label = 'Cluster 4')
plt.scatter(X[y_hc == 4, 0], X[y_hc == 4, 1], s = 100, c = 'magenta', label = 'Cluster 5')
plt.title('Clusters of customers')
plt.xlabel('Annual Income (k$)')
plt.ylabel('Spending Score (1-100)')
plt.legend()
plt.show()
```

**R**

```{r}
library(cluster)
clusplot(dataset,
         y_hc,
         lines = 0,
         shade = TRUE,
         color = TRUE,
         labels = 2,
         plotchar = FALSE,
         span = TRUE,
         main = paste('Clusters of customers'),
         xlab = 'Annual Income',
         ylab = 'Spending Score')
```
