# Association Rule Learning

## Apriori

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Data Preprocessing

**Python**

```{python}
dataset = pd.read_csv('Market_Basket_Optimisation.csv', header = None)
transactions = []
for i in range(0, 7501):
  transactions.append([str(dataset.values[i,j]) for j in range(0, 20)])
```

**R**

```{r}
# install.packages('arules')
library(arules)
dataset = read.csv('Market_Basket_Optimisation.csv', header = FALSE)
dataset = read.transactions('Market_Basket_Optimisation.csv', sep = ',', rm.duplicates = TRUE)
summary(dataset)
itemFrequencyPlot(dataset, topN = 10)
```

### Training the Apriori model on the dataset

**Python**

Run the following command in the terminal to install the apyori package: pip install apyori

```{python}
from apyori import apriori
rules = apriori(transactions = transactions, min_support = 0.003, min_confidence = 0.2, min_lift = 3, min_length = 2, max_length = 2)
```

**R**

```{r}
rules = apriori(data = dataset, parameter = list(support = 0.004, confidence = 0.2))
```

### Visualising the results

**Python**

Displaying the first results coming directly from the output of the apriori function:

```{python}
results = list(rules)
results
```

Putting the results well organised into a Pandas DataFrame:

```{python}
def inspect(results):
    lhs         = [tuple(result[2][0][0])[0] for result in results]
    rhs         = [tuple(result[2][0][1])[0] for result in results]
    supports    = [result[1] for result in results]
    confidences = [result[2][0][2] for result in results]
    lifts       = [result[2][0][3] for result in results]
    return list(zip(lhs, rhs, supports, confidences, lifts))
resultsinDataFrame = pd.DataFrame(inspect(results), columns = ['Left Hand Side', 'Right Hand Side', 'Support', 'Confidence', 'Lift'])
```

Displaying the results non sorted:

```{python}
resultsinDataFrame
```

Displaying the results sorted by descending lifts:

```{python}
resultsinDataFrame.nlargest(n = 10, columns = 'Lift')
```

**R**

```{r}
inspect(sort(rules, by = 'lift')[1:10])
```

## Eclat

Run the following command in the terminal to install the apyori package: pip install apyori

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Data Preprocessing

**Python**

```{python}
dataset = pd.read_csv('Market_Basket_Optimisation.csv', header = None)
transactions = []
for i in range(0, 7501):
  transactions.append([str(dataset.values[i,j]) for j in range(0, 20)])
```

**R**

```{r}
# install.packages('arules')
library(arules)
dataset = read.csv('Market_Basket_Optimisation.csv')
dataset = read.transactions('Market_Basket_Optimisation.csv', sep = ',', rm.duplicates = TRUE)
summary(dataset)
itemFrequencyPlot(dataset, topN = 10)
```

### Training the Eclat model on the dataset

**Python**

```{python}
from apyori import apriori
rules = apriori(transactions = transactions, min_support = 0.003, min_confidence = 0.2, min_lift = 3, min_length = 2, max_length = 2)
```

**R**

```{r}
rules = eclat(data = dataset, parameter = list(support = 0.003, minlen = 2))
```

### Visualising the results

**Python**

Displaying the first results coming directly from the output of the apriori function:

```{python}
results = list(rules)
results
```

Putting the results well organised into a Pandas DataFrame:

```{python}
def inspect(results):
    lhs         = [tuple(result[2][0][0])[0] for result in results]
    rhs         = [tuple(result[2][0][1])[0] for result in results]
    supports    = [result[1] for result in results]
    return list(zip(lhs, rhs, supports))
resultsinDataFrame = pd.DataFrame(inspect(results), columns = ['Product 1', 'Product 2', 'Support'])
```

Displaying the results sorted by descending supports:

```{python}
resultsinDataFrame.nlargest(n = 10, columns = 'Support')
```

**R**

```{r}
inspect(sort(rules, by = 'support')[1:10])
```
