# Model Selection & Boosting

## k-Fold Cross Validation/Grid Search

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Importing the dataset

**Python**

```{python}
dataset = pd.read_csv('Social_Network_Ads.csv')
X = dataset.iloc[:, :-1].values
y = dataset.iloc[:, -1].values
```

**R**

```{r}
dataset = read.csv('Social_Network_Ads.csv')
# dataset = dataset[3:5]
```

### Encoding the target feature as factor

**R**

```{r}
dataset$Purchased = factor(dataset$Purchased, levels = c(0, 1))
```

### Splitting the dataset into the Training set and Test set

**Python**

```{python}
from sklearn.model_selection import train_test_split
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size = 0.25, random_state = 0)
```

**R**

```{r}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Purchased, SplitRatio = 0.75)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

### Feature Scaling

**Python**

```{python}
from sklearn.preprocessing import StandardScaler
sc = StandardScaler()
X_train = sc.fit_transform(X_train)
X_test = sc.transform(X_test)
```

**R**

```{r}
training_set[-3] = scale(training_set[-3])
test_set[-3] = scale(test_set[-3])
```

### Training the Kernel SVM model on the Training set

**Python**

```{python}
from sklearn.svm import SVC
classifier = SVC(kernel = 'rbf', random_state = 0)
classifier.fit(X_train, y_train)
```

**R**

```{r}
# install.packages('e1071')
library(e1071)
classifier = svm(formula = Purchased ~ .,
                 data = training_set,
                 type = 'C-classification',
                 kernel = 'radial')
```

### Predicting the Test set results

**R**

```{r}
y_pred = predict(classifier, newdata = test_set[-3])
```

### Making the Confusion Matrix

**Python**

```{python}
from sklearn.metrics import confusion_matrix, accuracy_score
y_pred = classifier.predict(X_test)
cm = confusion_matrix(y_test, y_pred)
print(cm)
accuracy_score(y_test, y_pred)
```

**R**

```{r}
cm = table(test_set[, 3], y_pred)
```

### Applying k-Fold Cross Validation

**Python**

```{python}
from sklearn.model_selection import cross_val_score
accuracies = cross_val_score(estimator = classifier, X = X_train, y = y_train, cv = 10)
print("Accuracy: {:.2f} %".format(accuracies.mean()*100))
print("Standard Deviation: {:.2f} %".format(accuracies.std()*100))
```

**R**

```{r}
# install.packages('caret')
library(caret)
folds = createFolds(training_set$Purchased, k = 10)
cv = lapply(folds, function(x) {
  training_fold = training_set[-x, ]
  test_fold = training_set[x, ]
  classifier = svm(formula = Purchased ~ .,
                   data = training_fold,
                   type = 'C-classification',
                   kernel = 'radial')
  y_pred = predict(classifier, newdata = test_fold[-3])
  cm = table(test_fold[, 3], y_pred)
  accuracy = (cm[1,1] + cm[2,2]) / (cm[1,1] + cm[2,2] + cm[1,2] + cm[2,1])
  return(accuracy)
})
accuracy = mean(as.numeric(cv))
```

### Applying Grid Search to find the best model and the best parameters

**Python**

```{python}
from sklearn.model_selection import GridSearchCV
parameters = [{'C': [0.25, 0.5, 0.75, 1], 'kernel': ['linear']},
              {'C': [0.25, 0.5, 0.75, 1], 'kernel': ['rbf'], 'gamma': [0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9]}]
grid_search = GridSearchCV(estimator = classifier,
                           param_grid = parameters,
                           scoring = 'accuracy',
                           cv = 10,
                           n_jobs = -1)
grid_search.fit(X_train, y_train)
best_accuracy = grid_search.best_score_
best_parameters = grid_search.best_params_
print("Best Accuracy: {:.2f} %".format(best_accuracy*100))
print("Best Parameters:", best_parameters)
```

**R**

```{r}
# install.packages('caret')
library(caret)
classifier = train(form = Purchased ~ ., data = training_set, method = 'svmRadial')
classifier
classifier$bestTune
```

### Visualising the Training set results

**Python**

```{python}
from matplotlib.colors import ListedColormap
X_set, y_set = X_train, y_train
X1, X2 = np.meshgrid(np.arange(start = X_set[:, 0].min() - 1, stop = X_set[:, 0].max() + 1, step = 0.01),
                     np.arange(start = X_set[:, 1].min() - 1, stop = X_set[:, 1].max() + 1, step = 0.01))
plt.contourf(X1, X2, classifier.predict(np.array([X1.ravel(), X2.ravel()]).T).reshape(X1.shape),
             alpha = 0.75, cmap = ListedColormap(('red', 'green')))
plt.xlim(X1.min(), X1.max())
plt.ylim(X2.min(), X2.max())
for i, j in enumerate(np.unique(y_set)):
    plt.scatter(X_set[y_set == j, 0], X_set[y_set == j, 1],
                c = ListedColormap(('red', 'green'))(i), label = j)
plt.title('Kernel SVM (Training set)')
plt.xlabel('Age')
plt.ylabel('Estimated Salary')
plt.legend()
plt.show()
```

**R**

```{r, cache = TRUE}
library(ElemStatLearn)
set = training_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3],
     main = 'Kernel SVM (Training set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'springgreen3', 'tomato'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'green4', 'red3'))
```

### Visualising the Test set results

**Python**

```{python}
from matplotlib.colors import ListedColormap
X_set, y_set = X_test, y_test
X1, X2 = np.meshgrid(np.arange(start = X_set[:, 0].min() - 1, stop = X_set[:, 0].max() + 1, step = 0.01),
                     np.arange(start = X_set[:, 1].min() - 1, stop = X_set[:, 1].max() + 1, step = 0.01))
plt.contourf(X1, X2, classifier.predict(np.array([X1.ravel(), X2.ravel()]).T).reshape(X1.shape),
             alpha = 0.75, cmap = ListedColormap(('red', 'green')))
plt.xlim(X1.min(), X1.max())
plt.ylim(X2.min(), X2.max())
for i, j in enumerate(np.unique(y_set)):
    plt.scatter(X_set[y_set == j, 0], X_set[y_set == j, 1],
                c = ListedColormap(('red', 'green'))(i), label = j)
plt.title('Kernel SVM (Test set)')
plt.xlabel('Age')
plt.ylabel('Estimated Salary')
plt.legend()
plt.show()
```

**R**

```{r, cache = TRUE}
library(ElemStatLearn)
set = test_set
X1 = seq(min(set[, 1]) - 1, max(set[, 1]) + 1, by = 0.01)
X2 = seq(min(set[, 2]) - 1, max(set[, 2]) + 1, by = 0.01)
grid_set = expand.grid(X1, X2)
colnames(grid_set) = c('Age', 'EstimatedSalary')
y_grid = predict(classifier, newdata = grid_set)
plot(set[, -3], main = 'Kernel SVM (Test set)',
     xlab = 'Age', ylab = 'Estimated Salary',
     xlim = range(X1), ylim = range(X2))
contour(X1, X2, matrix(as.numeric(y_grid), length(X1), length(X2)), add = TRUE)
points(grid_set, pch = '.', col = ifelse(y_grid == 1, 'springgreen3', 'tomato'))
points(set, pch = 21, bg = ifelse(set[, 3] == 1, 'green4', 'red3'))
```

## XGBoost

### Importing the libraries

**Python**

```{python}
import numpy as np
import matplotlib.pyplot as plt
import pandas as pd
```

### Importing the dataset

**Python**

```{python}
dataset = pd.read_csv('Data.csv')
# dataset = pd.read_csv('Churn_Modelling.csv')
X = dataset.iloc[:, :-1].values
y = dataset.iloc[:, -1].values
```

**R**

```{r}
dataset = read.csv('Churn_Modelling.csv')
dataset = dataset[4:14]
```

### Encoding the categorical variables as factors

**R**

```{r}
dataset$Geography = as.numeric(factor(dataset$Geography,
                                      levels = c('France', 'Spain', 'Germany'),
                                      labels = c(1, 2, 3)))
dataset$Gender = as.numeric(factor(dataset$Gender,
                                   levels = c('Female', 'Male'),
                                   labels = c(1, 2)))
```

### Splitting the dataset into the Training set and Test set

**Python**

```{python}
from sklearn.model_selection import train_test_split
X_train, X_test, y_train, y_test = train_test_split(X, y, test_size = 0.2, random_state = 0)
```

**R**

```{r}
# install.packages('caTools')
library(caTools)
set.seed(123)
split = sample.split(dataset$Exited, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

### Training XGBoost on the Training set

**Python**

```{python}
from xgboost import XGBClassifier
classifier = XGBClassifier()
# classifier = XGBClassifier(use_label_encoder = False)
classifier.fit(X_train, y_train)
```

**R**

```{r}
# install.packages('xgboost')
library(xgboost)
classifier = xgboost(data = as.matrix(training_set[-11]), label = training_set$Exited, nrounds = 10)
```

### Predicting the Test set results

**R**

```{r}
y_pred = predict(classifier, newdata = as.matrix(test_set[-11]))
y_pred = (y_pred >= 0.5)
```

### Making the Confusion Matrix

**Python**

```{python}
from sklearn.metrics import confusion_matrix, accuracy_score
y_pred = classifier.predict(X_test)
cm = confusion_matrix(y_test, y_pred)
print(cm)
accuracy_score(y_test, y_pred)
```

**R**

```{r}
cm = table(test_set[, 11], y_pred)
```

### Applying k-Fold Cross Validation

**Python**

```{python}
from sklearn.model_selection import cross_val_score
accuracies = cross_val_score(estimator = classifier, X = X_train, y = y_train, cv = 10)
print("Accuracy: {:.2f} %".format(accuracies.mean()*100))
print("Standard Deviation: {:.2f} %".format(accuracies.std()*100))
```

**R**

```{r}
# install.packages('caret')
library(caret)
folds = createFolds(training_set$Exited, k = 10)
cv = lapply(folds, function(x) {
  training_fold = training_set[-x, ]
  test_fold = training_set[x, ]
  classifier = xgboost(data = as.matrix(training_fold[-11]), label = training_fold$Exited, nrounds = 10)
  y_pred = predict(classifier, newdata = as.matrix(test_fold[-11]))
  y_pred = (y_pred >= 0.5)
  cm = table(test_fold[, 11], y_pred)
  accuracy = (cm[1,1] + cm[2,2]) / (cm[1,1] + cm[2,2] + cm[1,2] + cm[2,1])
  return(accuracy)
})
accuracy = mean(as.numeric(cv))
```
